Application-Level Regression Testing Framework using Jenkins

### 2017-04-04 manuscript/manuscript.tex
Starting tweaking Anatomy section.

\begin{abstract}
This paper will explore the challenges of regression testing and monitoring of large scale systems such as NCSA'€™s Blue Waters. 
Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. 
Jenkins was chosen for its versatility, large user base, and multitudes of plugins including plotting test results over time. 
We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). 
Not only does Jenkins have the ability to store historical data, but it can also send email or text messages based on results of a test. 
Other requirements we had included two-factor authentication for accessing the Jenkins GUI with administrator privileges and account management through LDAP. 
In this paper we describe our experience in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
\end{abstract}

@@

Monitoring large and complex high-performance computing systems have many challenges. 
Layers and multiple versions of the software stack, system-level configurations, (parallel) file systems, diversity in user need and usage, and variable network traffic all interact to increase the system's complexity. 
Although there exist monitoring systems for each of these components, they often do not capture the behavior of the system in aggregate, which in fact is what users and their applications experience. 
Therefore an application-level system monitoring framework is needed to give us a more complete picture of the system behavior.

@@

The benefit of this method is that one can basically treat the nodes as a local environment in Jenkins, while having access to the HPC environment. 
For example, each node would have access to the parallel lustre filesystem mounted by the HPC system (even if Jenkins master itself does not, being only a small separate VM). 
Each node can define its lustre filesystem as its build and test workspace. 
Yet Jenkins automatically manages all communication with the nodes such that files (e.g. plot data, test output) generated on the lustre filesystem are readable from Jenkins without the explicit remote copy (i.e. via SCP). 
Another example is that one can have Jenkins checkout or clone code from a remote repository (e.g. using Subversion or Git) and the copy will be automatically available on the lustre filesystem defined as the workspace of that node. 
These integration benefits make building Jenkins projects more seamless.

@@

Optionally, one may allow non-authenticated, ''read-only`` access to the Jenkins dashboard over regular (non-secure) HTTP connections. 
Jenkins' own authorization mechanism can be used to control this access, but we can also add Apache HTTP directives for further security, limiting to \texttt{GET} requests only. 
To achieve this, we created the file \texttt{/etc/httpd/conf.d/vhosts.conf} with the following content:
\begin{lstlisting}

@@

\section{Authenticating with One-Time Password}

Although Jenkins supplies its own authentication mechanism with its built-in user and password database, we feel that it is inadequate for securing our instance. 
The default Jenkins authentication setup is also unfortunate, in which it allows anyone to self-register creating their own username and password\footnote{This is perhaps another artifact of Jenkins setup intended for intranet environment}. 
We wanted instead to use our One-Time Password (OTP) infrastructure with RSA SecurID (FIXME: Add references https://www.rsa.com/en-us/products/rsa-securid-suite, https://en.wikipedia.org/wiki/RSA_SecurID) token for authentication. 
In this section we describe how we accomplished that.

@@

\begin{lstlisting}
#-- OTP for Jenkins SSL connection
DefineExternalAuth pwauth+session pipe \
/usr/local/bin/BasicAuthOTPSession.py

@@

\section{Authentication and Authorization}
\label{sec:AuthenticationAuthorization}

%\subsection{Security Considerations}
%CUT THE NEXT TWO PARAGRAPHS AND DESCRIPTION OF CONFIG FILES OR REDUCE SINCE IT IS COVERED ABOVE --GALEN
%Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome. 
%Blue Waters is an OTP only restricted access system. 
%Jenkins has the ability to execute user-level commands on our login nodes. 
%It also has some unfortunate default settings. 
%The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password. 
%Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once signed in, you have full admin access to the Jenkins system instance. 
% This required us initially to test the deployment with our TDS. 
%This resulted in the following requirement: restricted OTP access to the physical system hosting Jenkins. 
%In addition, OTP only access to the Jenkins GUI command console must be contained within our IP space. 
% The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.

%\subsection{Configuration Choices}
%The Jenkins instance was deployed on a vSphere managed VM running Centos 6.8. The VM allows restricted host-based ssh access from two secure OTP only administrative systems. The Jenkins GUI presented additional challenges. The Jenkins GUI is configured to log in as a standard user account with password-less access (commands to the login nodes can be input via Jenkins GUI) using ssh keys scoped to the VM. We restrict access to the physical VM (bwjenkins) and the Jenkins GUI utilizing iptables, SSL and OTP.  Jenkins is configured to listen on port 8080 by default and we restricted it to localhost only. A reverse proxy was configured to run Jenkins behind Apache HTTP Server and SSL for access to the administrative console. With this reverse proxy, apache accepts requests on port 80 and 443 of bwjenkins.ncsa.illinois.edu and forwards them to the Jenkins web server at localhost which is now firewall protected. Most of this configuration is in /etc/httpd/conf.d/ssl.conf. Anonymous access to the Jenkins GUI was allowed for limited read only view of test status and historical plots. The Anonymous access view is not restricted.

%\begin{lstlisting}
%NOTE: Install mod_authnz_external Apache package

%(Jenkins sever configuration file snippets below)

%/etc/ssh/sshd_config:
%Match Host bwbh1.ncsa.illinois.edu,
%bwbh2.ncsa.illinois.edu
%HostbasedAuthentication yes

@@

%/etc/httpd/conf.d/ssl.conf:
% # -- The following sets ReverseProxy for Jenkins
%ProxyRequests       Off
%ProxyPreserveHost   On
%AllowEncodedSlashes On
%<Proxy *>
%Order deny,allow
%Allow from all
%</Proxy>
%ProxyPass       / http://localhost:8080/ nocanon
%ProxyPassReverse / http://localhost:8080/
%ProxyPassReverse / http://bwjenkins.ncsa.illinois.edu/
%RequestHeader set X-Forwarded-Proto "https"
%RequestHeader set X-Forwarded-Port "443"

%\begin{lstlisting}
% # -- OTP for Jenkins SSL connection
%DefineExternalAuth pwauth+session pipe 
%/usr/local/bin/pwauth+session
%<LocationMatch / > 
%AuthType Basic
%AuthBasicProvider external
%AuthName "NCSA RSA OTP login" 
%AuthExternal pwauth+session
%require valid-user  
%RequestHeader unset "X-Forwarded-User"
%RequestHeader set "X-Forwarded-User" (REMOTE_USER)
%</LocationMatch>
 %
%
%/usr/local/bin/pwauth+session(OTP caching): 
%https://github.com/reubendb/BasicAuthOTPSession
%/blob/master/BasicAuthOTPSession.py#L1
%
 % 
%/etc/pam.d/pwauth (for OTP):
 %#%PAM-1.0
%auth  required  /lib64/security/pam_securid.so
%account  include  password-auth
%\end{lstlisting}
%/etc/sysconfig/jenkins (restrict to localhost):
%JENKINS_PORT="8080"
%JENKINS_LISTEN_ADDRESS=127.0.0.1
%\end{lstlisting}
\subsection{LDAP with Jenkins} 
%To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}
To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
At first this failed because our LDAP is using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
We had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

\subsection{Configure Global Security}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
\caption{ Configure Global Security }
\label{fig:Configure-Global-Security}
\end{figure}
We allow access by username and LDAP groups. The permissions can be scoped for individuals and groups. An example is removing Job delete permissions to prevent one user or group from deleting each other's jobs.

\section{Anatomy of A Test}
\label{sec:TestAnatomy}
New software projects are required to be tested on our test and development system (TDS) and approved before deployment on Blue Waters and this is one of our key best practices. 
 Once a test is deployed it is assigned to a specific Jenkins tab via the "Edit View" link associated with that tab. 
 Tests still in development reside in the "All" tab view until they have been peer reviewed by at least one other test developer.
\subsection{test description}
We require a description for each test to describe: what is tested, resources used by the test, intent of the test, and scheduling frequency.
\subsection{limits log files}
The Jenkins test VM filled to capacity after the first few weeks of intensive use and an influx of several new tests that output long source code build detail. 
 We retroactively modified all tests to limit the number of old build logs retained (max 50 for most tests).

\subsection{ssh to a login host}
There are several target ssh hosts which may be selected from our instance: the TDS (JYC), the main system, and the new software deployment login node within the main system. 
 None of our tests run locally within the Jenkins VM.
\subsection{run shell commands}
A test is composed of shell command and where possible we try to be as transparent with our test construction as possible. 
 We prefer commands in the Jenkins configuration over running a script in the filesystem on the remote ssh target. 
 Scripts that are remote run with verbose mode or are displayed via "cat -n" to save output to the Jenkins console log and make for simpler debugging when a test fails.
\subsubsection{test completes on login node}
Some tests run only on the ssh login node and return more or less immediately. 
 Examples include tests for batch system functionality, ssh functionality, and filesystem functionality. 
 These tests are very similar in style to unit tests which target a limited set of functionality.
\subsubsection{test is submitted to batch system}
More comprehensive tests typically build and run an application or benchmark through the batch system. 
 These tests exercise multiple aspects of the system: (filesystem, compilers and modules, high-speed network, external connectivity to the internet...). 
 They block to completion so that we do not overburden the batch system with tests. 
 Unlike tests that run entirely on a login node, completion time can be highly variable depending on the queue depth and available backfill windows for the batch system.
\subsection{post test actions}
\subsubsection{scp files back to Jenkins host}
Most comprehensive tests produce output that we use when debugging a failed test. 
 They may also produce plot data. 
 These files are copied back to the Jenkins host so that they can be viewed and/or incorporated into the plot feature of Jenkins.
\subsubsection{plots}
Successful tests save plot files and contribute a new data point to a plot. 
 The Jenkins server accumulates the data as rows in a spreadsheet (under /var/lib/jenkins/jobs/ ) and plots them via the "Plots" link for a test.
\subsection{email notification}
When the state of a test changes, email notification is sent to the test owner. 
 As a best practice we also use the email notification as a method of tracking authorship and each test has an email owner even if notifications are disabled for the test.

\section{SWTools Integration}
\label{sec:SWToolsIntegration}
\subsection{SWTools with Jenkins}
%\begin{figure}[H]
%\centering
%\includegraphics[width=0.5\textwidth]{swtools-Jenkins}
%\caption{ Use SWTools with Jenkins }
%\label{fig:swtools-jenkins}
%\end{figure}

\subsection{SWTools with Lammps}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{swtools-lammps}
\caption{ SWTools with Lammps }
\label{fig:swtools-lammps}
\end{figure}

@@

\subsection{special projects}
The initial display tabs in our Jenkins instance are used to group tests and we add tabs for special projects.   For example we clone existing tests for evaluating a new software stack on our test login node (h2ologin4).   Our TDS (JYC) has a separate set of tests from our production system and is used as our Jenkins development mule.  The sustained petascale performance benchmarks (SPP) are in their own tab because they run at scale and are only run on-demand by staff (not scheduled by Jenkins ).
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{tabs-display}
\caption{ tabs for project areas }
\label{fig:tabs-display}
\end{figure}

@@

We typically run the latest Programming Environment (PE) on our TDS. Our production login nodes and the supercomputer have the latest PE installed as non default during initial testing and it can be loaded by modulefile selection. Our test login node is utilized for testing new software stacks and changes to the login environment that are independent of our production resources. Therefore Jenkins Projects tailored for each environment allow for regression testing of the current production as well as pre-production user-level environments.

>>>>

\begin{abstract}
This paper explores the challenges of regression testing and monitoring of large scale systems such as NCSA's Blue Waters. 
Our goal was to come up with an automated solution for running user-level regression tests to evaluate system usability and performance. 
Jenkins was chosen for its versatility, large user base, and multitudes of plugins including plotting test results over time. 
We utilize these plots to track trends and alert us to system-level issues before they are reported by our partners (users). 
Not only does Jenkins have the ability to store historical data, but it can also send email or text messages based on results of a test. 
Other requirements we had included two-factor authentication for accessing the Jenkins GUI with administrator privileges and account management through LDAP. 
In this paper we describe our experience in deploying Jenkins as a user-level system-wide regression testing and monitoring framework for Blue Waters.
\end{abstract}

@@

Monitoring large and complex high-performance computing systems has many challenges. 
Layers and multiple versions of the software stack, system-level configurations, (parallel) file systems, diversity in user need and usage, and variable network traffic all interact to increase the system's complexity. 
Although there exist monitoring systems for each of these components, they often do not capture the behavior of the system in aggregate, which in fact is what users and their applications experience. 
Therefore an application-level system monitoring framework is needed to give us a more complete picture of the system behavior.

@@

The benefit of this method is that one can basically treat the nodes as a local environment in Jenkins, while having access to the HPC environment. 
For example, each node would have access to the parallel lustre filesystem mounted by the HPC system (even if Jenkins master itself does not, being only a small separate VM). 
Each node can define its lustre filesystem as its build and test workspace. 
Yet Jenkins automatically manages all communication with the nodes such that files (e.g. plot data, test output) generated on the lustre filesystem are readable from Jenkins without the explicit remote copy (i.e. via SCP). 
Another example is that one can have Jenkins checkout or clone code from remote a repository (e.g. using Subversion or Git) and the copy will be automatically available on the lustre filesystem defined as the workspace of that node. 
These integration benefits make building Jenkins projects more seamless.

@@

Optionally, one may allow non-authenticated, ''read-only`` access to the Jenkins dashboard over regular (non-secure) HTTP connections. 
Jenkins' own authorization mechanism can be used to control this access, but we can also add Apache HTTP directives for further security, limiting \texttt{GET} requests. 
To achieve this, we created the file \texttt{/etc/httpd/conf.d/vhosts.conf} with the following content:
\begin{lstlisting}

@@

\subsection{Authenticating with One-Time Password}

Although Jenkins supplies its own authentication mechanism with its built-in user and password database, we feel that it is inadequate for securing our instance. 
The default Jenkins authentication setup is also unfortunate, in which it allows anyone to self-register creating their own username and password \footnote{This is perhaps another artifact of Jenkins setup intended to intranet environment.} 
We wanted instead to use our One-Time Password (OTP) infrastructure with RSA SecurID (FIXME: Add references https://www.rsa.com/en-us/products/rsa-securid-suite, https://en.wikipedia.org/wiki/RSA_SecurID) token for authentication. 
In this section we describe how we accomplished that.

@@

\begin{lstlisting}
#-- OTP for Jenkins SSL connection
DefineExternalAuth pwauth+session pipe 
  /usr/local/bin/BasicAuthOTPSession.py

@@

\subsection{Authorization and Access Control}
\label{subsec:authorization}

Jenkins default authorization allows logged in (authenticated) users to have full control. 
We wanted a more fine-grained access control to our instance and therefore selected the ''matrix-based security`` option (see Figure \ref{fig:jenkinsAuthorization}). Using this option we can limit what access individual users and groups have to our Jenkins instance. 
For example we restrict most users (other than admin users) from having the ''Job Delete`` permission to prevent one user or group from deleting each other's jobs.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{Configure-Global-Security}
\caption{Jenkins fine-grained authorization.}
\label{fig:jenkinsAuthorization}
\end{figure}

We use the built-in LDAP plugin to query our LDAP server what group a user belongs to.
This greatly simplifies managing the authorization since it can be done based on groups rather than just individual users. 
The LDAP plugins gets the user information from the HTTP header passed by the reverse proxy set up. 
Figure \ref{fig:LDAP-Jenkins} shows the screenshot of our LDAP configuration within Jenkins interface.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{Using LDAP with Jenkins.}
\label{fig:LDAP-Jenkins}
\end{figure}

Since Jenkins allows one to enter arbitrarily command to be executed on login nodes, we want to further mitigate security risk via firewall rules. 
In our installation, we only allow IP address originating from our institution block to access the secure HTTP portion and authenticate to access Jenkins. 
At NCSA, the non secure, read-only, HTTP portion is accessible from anywhere. 
At NICS, this access is only allowed from the institution IP block only.

@@

\section{Anatomy of A Test Application}
\label{sec:TestAnatomy}
An application test is a Jenkins project. In this section we describe what a project typically consist of.

% New software projects are required to be tested on our TDS and approved before deployment on Blue Waters and this is one of our key best practices. 
%  Once a test is deployed it is assigned to a specific Jenkins tab via the "Edit View" link associated with that tab. 
%  Tests still in development reside in the "All" tab view until they have been peer reviewed by at least one other test developer.

\subsection{Description}
We require a description for each project to describe: what is tested, resources used by the test, intent of the test, and scheduling frequency.

\subsection{Limiting Retained Build Log}
The Jenkins VM filled to capacity after the first few weeks of intensive use and an influx of several new projects that output long source code build detail. 
We retroactively modified all projects to limit the number of old build logs retained (maximum 50 for most projects).

\subsection{SSH to a Login Host}
There are several target ssh hosts which may be selected from our instance: the test rack JYC, the main system, and the new software deployment login node within the main system. 
 None of our tests run locally within the Jenkins VM.
\subsection{run shell commands}
A test is composed of shell command and where possible we try to be as transparent with our test construction as possible. 
We prefer commands in the Jenkins configuration over running a script in the filesystem on the remote ssh target. 
Scripts that are remote run with verbose mode or are displayed via "cat -n" to save output to the Jenkins console log and make for simpler debugging when a test fails.
\subsubsection{test completes on login node}
Some tests run only on the ssh login node and return more or less immediately. 
 Examples include tests for batch system functionality, ssh functionality, and filesystem functionality. 
 These tests are very similar in style to unit tests which target a limited set of functionality.
\subsubsection{test is submitted to batch system}
More comprehensive tests typically build and run an application or benchmark through the batch system. 
 These tests exercise multiple aspects of the system: (filesystem, compilers and modules, high-speed network, external connectivity to the internet...). 
 They block to completion so that we do not overburden the batch system with tests. 
 Unlike tests that run entirely on a login node, completion time can be highly variable depending on the queue depth and available backfill windows for the batch system.
\subsection{post test actions}
\subsubsection{scp files back to Jenkins host}
Most comprehensive tests produce output that we use when debugging a failed test. 
 They may also produce plot data. 
 These files are copied back to the Jenkins host so that they can be viewed and/or incorporated into the plot feature of Jenkins.
\subsubsection{plots}
Successful tests save plot files and contribute a new data point to a plot. 
 The Jenkins server accumulates the data as rows in a spreadsheet (under /var/lib/jenkins/jobs/ ) and plots them via the "Plots" link for a test.
\subsection{email notification}
When the state of a test changes, email notification is sent to the test owner. 
 As a best practice we also use the email notification as a method of tracking authorship and each test has an email owner even if notifications are disabled for the test.

@@

\subsection{special projects}
The initial display tabs in our Jenkins instance are used to group tests and we add tabs for special projects.   For example we clone existing tests for evaluating a new software stack on our test login node.   Our test rack has a separate set of tests from our production system and is used as our Jenkins development mule.  The sustained petascale performance benchmarks are in their own tab because they run at scale and are only run on-demand by staff (not scheduled by Jenkins ).
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{tabs-display}
\caption{ tabs for project areas }
\label{fig:tabs-display}
\end{figure}

@@

We typically run the latest Programming Environment (PE) on our TDS. Our production login nodes and the supercomputer have the latest PE installed as non default during initial testing and it can be loaded by modulefile selection. Our test login node (Bright Cluster Provisioned EsLogin) is utilized for testing new software stacks and changes to the login environment that are independent of our production resources. Therefore Jenkins Projects tailored for each environment allow for regression testing of the current production as well as pre-production user-level environments.
